Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
add zlog seq eval
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\subsection{MDS as ZLog Sequencer}\label{mds-as-zlog-sequencer}

@@

\begin{figure}[htbp]
\centering
\includegraphics{figures/caps-delay-thruput.png}
\caption{Forcing the client to drop their capabilities later (delay)
improves throughput}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{figures/caps-delay-latency.png}
\caption{But if the clients hold their capabilities longer, it hurts
latency for everyone.}
\end{figure}

>>>>

\subsection{ZLog Sequencer}

We evaluated the performance of the ZLog Sequencer implemented in several
different configurations by showing a trade-off between aggregate throughput
achieved (shown in Figure~\ref{fig:captp}), and latency distribution (shown in
Figure~\ref{fig:capcdf}).

In Figure~\ref{fig:captp} the highest throughput labeled $1C$ shows that a
single client caching the sequencer resource may obtain new sequences at a rate
of nearly 6 million positions per second. This is not surprising given that all
state is cached locally in the client. When this resource is shared between two
clients, the MDS uses a best-effort approach to granting the sequencer resource
to each client (value $2C,BE$). This sharing has a large impact on performance,
as shown by the nearly three orders of magnitude drop off in throughput.

While a best-effort approach to sharing capabilities makes sense for a file
system client, throughput drops significantly with two clients as the majority
of the time neither client has the capapbitility as it ping-pongs between
clients. This observation reveals a tuning parameter: how long a client
maintains its capapbility lease. In throughputs labeled $2C,<time>$ we show
aggregate throughput as we decrease the amount of time that a client holds its
lease before responding to a request for the capapbility.  At lease times as
low as 10ms throughputs achieve a significant proportion of the locally cached
throughput.

While the batching mechanism can achieve high-throughput, it is not appropriate
for applications that require predictable latency. The throughput in
Figure~\ref{fig:captp} labeled $2C,ZLog$ corresponds to a centeralized
sequencer implementation. While throughput is lower for two clients (because of
the synchronous network round-trip required for each request),
Figure~\ref{fig:capcdf} shows that this approach achieves more predicable
latency compared to all other approaches except for the single client locally
cached mode.

@@

\begin{figure}[htbp]
\centering
\includegraphics{figures/caps-delay-thruput.png}
\caption{Sequencer throughput by reusing various services.
The highest performance is achieved using a single client with
exclusive, cacheable priviledge. Round-robin sharing of the sequencer
resource is affected by the amount of time the resource is held,
with best-effort performing the worst.}
\label{fig:captp}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{figures/caps-delay-latency.png}
\caption{But if the clients hold their capabilities longer, it hurts
latency for everyone.}
\label{fig:capcdf}
\end{figure}

@@
